---
title: "Selected Graph Options"
output: html_document
params:
  rotateXLabels: NA
  yAxisLabel: NA
  xAxisLabel: NA
  font: NA
  xAxisTitleFontSize: NA
  yAxisTitleFontSize: NA
  xAxisTextFontSize: NA
  yAxisTextFontSize: NA
  colourScheme: NA
  plotType: NA
  significance: NA
  labelSize: NA
  bracketThickness: NA
  tipLength: NA
  stepIncrease: NA
  hideNS: NA
  pValuePrefix: NA
  pValueDecimals: NA
  removeLeadingZero: NA
  errorBarType: NA
  startAtZero: NA
  errorBarWidth: NA
  errorBarWidthdot: NA
  errorBarThickness: NA
  errorBarThicknessdot: NA
  errorBarColour: NA
  averageLineWidth: NA
  averageLineThickness: NA
  averageLineColour: NA
  fillOrBorder: NA
  pointSize: NA
  pointSizedot: NA
  pointSpacing: NA
  changeToPairedShapes: NA
  shapeOutlineThickness: NA
  pointSpread: NA
  seedNumber: NA
  fileFormat: NA
  dpi: NA
  width: NA
  height: NA
---


<style>
h1, h2, h3, h4, h5, h6 {
  color: #00359c;
}
</style>

```{r setup, include=FALSE}
# Load necessary libraries
library(knitr)
library(rmarkdown)

```

### Your selected graph options

* Rotate x-axis labels: `r params$rotateXLabels`
* Y-axis label: `r params$yAxisLabel`
* X-axis label: `r params$xAxisLabel`
* Font: `r params$font`
* X-axis title font size: `r params$xAxisTitleFontSize`
* Y-axis title font size: `r params$yAxisTitleFontSize`
* X-axis text font size: `r params$xAxisTextFontSize`
* Y-axis text font size: `r params$yAxisTextFontSize`
* Colour scheme: `r params$colourScheme`
* Plot type: `r switch(params$plotType,
                      "dot" = "Scatter Plot",
                      "dot_group" = "Grouped Scatter Plot",
                      "column" = "Column Graph",
                      params$plotType)` 

#### Significance options

* Significance?: `r switch(params$significance,
                           "asterix" = "Asterisk",
                           "pval" = "P-Value",
                           "cld" = "Compact Letter Display",
                           params$significance)`
* Label size: `r params$labelSize`
* Bracket thickness: `r params$bracketThickness`
* Tip length: `r params$tipLength`
* Step increase: `r params$stepIncrease`
* Hide ns: `r params$hideNS`
* P value prefix: `r params$pValuePrefix`
* P value decimals: `r params$pValueDecimals`
* Remove leading 0: `r params$removeLeadingZero`

#### Error Bars

* Error bar type: `r switch(params$errorBarType,
                           "se" = "Standard Error",
                           "sd" = "Standard Deviation",
                           "ci" = "95% Confidence Interval",
                           params$errorBarType)`
* Start at y = 0: `r params$startAtZero`
* Error bar colour: `r params$errorBarColour`
* Average line width (dot graph): `r params$averageLineWidth`
* Average line thickness (dot graph): `r params$averageLineThickness`
* Average line colour (dot graph): `r params$averageLineColour`
* Error bar width (column graph): `r params$errorBarWidth`
* Error bar thickness (column graph): `r params$errorBarThickness`
* Error bar width (dot graph): `r params$errorBarWidthdot`
* Error bar thickness (dot graph): `r params$errorBarThicknessdot`


#### Point Design

* Fill or Border (column graph): `r params$fillOrBorder`
* Point size (column graph): `r params$pointSize`
* Point size (dot graph): `r params$pointSizedot`
* Point Spacing (column graph): `r params$pointSpacing`
* Change to paired shapes: `r params$changeToPairedShapes`
* Shape outline thickness: `r params$shapeOutlineThickness`
* Point spread: `r params$pointSpread`
* Seed number: `r params$seedNumber`

#### Download Options

* File format: `r params$fileFormat`
* DPI: `r params$dpi`
* Width (in): `r params$width`
* Height (in): `r params$height`

#### **Contact**

If you have found any issues with this report, or want to suggest improvements, please contact the developer [Marnie](mailto:mlm715@uowmail.edu.au) or [here](mailto:mmaddock@uow.edu.au). Issues, or requests for features can also be added in the `Issues` tab on [GitHub](https://github.com/MarnieMaddock/ProntoPCR/issues). Note Colour Scheme suggestions for graphs can also be sent to [Marnie](mailto:mlm715@uowmail.edu.au?subject=ProntoPCR Colour Request&body=Hi, I have a colour scheme request. Here is a list of colours in order. Please use hex codes, e.g. #000000, #63b8ff:).


```{r footer, echo=FALSE, results = 'hide'}
# Check if the app is running on shinyapps.io by checking the SHINY_PORT environment variable
is_local <- Sys.getenv("SHINY_PORT") == ""

if (is_local) {
  # This block will only run when the app is running locally
  footer_svg_path <- system.file("www", "footer.svg", package = "ProntoPCR")
  
  if (file.exists(footer_svg_path)) {
    knitr::include_graphics(footer_svg_path)
  } else {
    NULL
  }
} else {
  # You can print a message or leave it blank for shinyapps.io deployment
  NULL
}

```

