---
title: "Statistics Report"
output: html_document
params:
  analysisType: NA
  selectedSamples: NA
  selectedGene: NA
  descTable: NA
  shapiroData: NA
  resFitPlot: NA
  qqPlotGraph: NA
  densityPlot: NA
  levene: NA
  logTransformed: NA
  testResultData: NA
  cldData: NA
  posthocData: NA
  testName: NA
  postHocName: NA

---


<style>
h1, h2, h3, h4, h5, h6 {
  color: #00359c;
}
</style>


```{r setup_stats, include=FALSE}
#packages for rmakrdown
library(kableExtra)

# Get the full path to the footer.svg image within the package
# footer_svg_path <- system.file("rmd_templates", "footer.svg", package = "ProntoPCR")
# if (file.exists(footer_svg_path)) {
#   knitr::include_graphics(footer_svg_path)
# } else {
#   "Footer image not found."
# }
```

### **ProntoPCR**

All statistics within the ProntoPCR app were performed in the R programming language. For more detailed information on the specifics of the statistical tests used, please refer to the documentation provided in the associated github page (INSERT VIGNETTE HERE), or refer to the source code [GitHub](https://github.com/MarnieMaddock/ProntoPCR).


### **Your Data**

This is the statistics report for the following: `r params$analysisType`, samples: `r paste(params$selectedSamples, collapse = ", ")`, and gene: `r params$selectedGene`.

### **Descriptive Statistics**

```{r descTable, echo = FALSE, results='asis'}
if(!is.null(params$descTable)) {
  knitr::kable(params$descTable, format = "html") %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
} else {
  cat("Descriptive statistics not selected.")
}


```

### **Normality Tests**


#### **Shapiro-Wilk Test**
```{r shapiroTable, echo = FALSE, results='asis'}
if (!is.null(params$shapiroData)) {
  # Create a formatted version of the shapiroData
  shapiroDataFormatted <- params$shapiroData
  
  # Format numeric columns to 10 decimal places
  shapiroDataFormatted$W <- format(shapiroDataFormatted$W, digits = 6, nsmall = 6)
  shapiroDataFormatted$P_value <- format(shapiroDataFormatted$P_value, digits = 6, nsmall = 6)
  
  knitr::kable(shapiroDataFormatted, format = "html") %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
} else {
  cat("Shapiro-Wilk test not selected.")
}
```

#### **Residuals vs Fitted Plot**
```{r resFitPlot, echo = FALSE, results='asis'}
if (!is.null(params$resFitPlot)) {
  print(params$resFitPlot)
} else {
  cat("Residuals vs Fitted plot not selected.")
}

```

#### **QQ-Plot**
```{r qqPlot, echo = FALSE, results='asis'}
if (!is.null(params$qqPlotGraph)) {
#if (!is.null(params$qqPlotGraph$layers)) {
  print(params$qqPlotGraph)
} else {
  cat("QQ-Plot not selected.")
}
```


#### **Density Plot**
```{r densityPlot, echo = FALSE, results='asis'}
if (!is.null(params$densityPlot)) {
#if (!is.null(params$densityPlot$layers)) {
  print(params$densityPlot)
} else {
  cat("Density plot not selected.")
}
```



### **Homogeneity of Variance**

#### **Levene's Test**
```{r levene, echo = FALSE, results='asis'}
if (!is.null(params$levene)) {
  knitr::kable(params$levene, format = "html") %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
} else {
  cat("Levene's test not selected.")
}
```



### **Log transformation?**

```{r log-transform-message, echo=FALSE, results='asis'}
if (!params$logTransformed) {
  cat("This data was ***not*** log transformed.")
} else {
  cat("This data was log transformed.")
}
```



### **Group Comparisons**
You selected a `r params$testName` test.


```{r comparison-results, echo=FALSE, results='asis'}
if (!is.null(params$testResultData)) {
  knitr::kable(params$testResultData, format = "html") %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
} else {
  cat("Group comparison test not selected.")
}
```


### **Post-Hoc Tests**
Reminder, post-hoc tests are only valid if the group comparison test has a p value < 0.05. `r params$postHocName`
```{r posthoc, echo=FALSE, results='asis'}
if (!is.null(params$posthocData)) {
  knitr::kable(params$posthocData, format = "html") %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
} else {
  cat("Post-hoc test not selected.")
}
```


#### **Compact Letter Notation**
Groups with the same letter are not significantly different from each other.
```{r cldTable, echo=FALSE, results='asis'}
if (!is.null(params$cldData)) {
  knitr::kable(params$cldData, format = "html") %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
} else {
  cat("Compact Letter Notation not selected.")
}
```

### **Contact**

If you have found any issues with this report, or want to suggest improvements, please contact the developer [Marnie](mailto:mlm715@uowmail.edu.au) or [here](mailto:mmaddock@uow.edu.au). Issues, or requests for features can also be added in the `Issues` tab on [GitHub](https://github.com/MarnieMaddock/ProntoPCR/issues). 

```{r footer, echo=FALSE}
# # Copy the footer.svg to a temporary directory
# footer_svg_path <- system.file("www", "footer.svg", package = "ProntoPCR")
# temp_footer_path <- file.path(tempdir(), "footer.svg")
# 
# # If the footer exists, copy it to the temp folder and display it
# if (file.exists(footer_svg_path)) {
#   file.copy(footer_svg_path, temp_footer_path, overwrite = TRUE)
#   knitr::include_graphics(temp_footer_path)
# } else {
#   "Footer image not found."
# }

footer_svg_path <- system.file("inst/rmd_templates", "footer.svg", package = "ProntoPCR")
#footer_svg_path <- system.file("www", "footer.svg", package = "ProntoPCR")
if (file.exists(footer_svg_path)) {
  knitr::include_graphics(footer_svg_path)
} else {
  "Footer image not found."
}
```



