---
title: "Statistics Report"
output: html_document
params:
  analysisType: NA
  selectedSamples: NA
  selectedGene: NA
  sampleSizeTable: NA
  shapiroData: NA
  qqPlotGraph: NA
  densityPlot: NA
  leveneData: NA
  logTransformed: NA
  testResultData: NA
  cldData: NA
  posthocData: NA
  testName: NA
  postHocName: NA
---
```{r setup, include=FALSE}
#packages for app
library(shiny)
library(rmarkdown)
library(readr)
library(DT)
library(tidyverse)
library(datawizard)
library(purrr)
library(ggplot2)
library(ggbeeswarm)
library(ggpubr)
library(bslib)
library(ggtext)
library(shinyjs)
library(car) 
library(multcomp) 
library(dplyr)
library(rlang)
library(broom)
library(DescTools)
library(FSA)
library(conover.test)
library(multcompView)

source("module_download.R")
source("utils_downloadGraphHandler.R")
source("about.R")
source("example_data_text.R")
source("utils_getColourSchemes.R")
#Stats functions
source("utils_performComparisonTests.R")
source("utils_performCLD.R")
source("utils_performTukeyPostHoc.R")
source("utils_performPostHoc.R")
source("utils_performDunnPostHoc.R")
source("utils_performConoverPostHoc.R")
#Graph functions
source("utils_graphTheme.R")
source("utils_getColourSchemes.R")
#packages for rmakrdown
library(kableExtra)
```
### **FASTqPCR**

All statistics within the FASTqPCR app were performed in the R programming language. For more detailed information on the specifics of the statistical tests used, please refer to the documentation provided in the associated github page (INSERT VIGNETTE HERE), or refer to the source code [GitHub](https://github.com/MarnieMaddock/FASTqPCR).

### **Your Data**

This is the statistics report for the following: `r params$analysisType`, samples: `r paste(params$selectedSamples, collapse = ", ")`, and gene: `r params$selectedGene`.

### **Sample Size Table**
```{r tableOutput, echo = FALSE, results='asis'}
if (!is.null(params$sampleSizeTable)) {
knitr::kable(params$sampleSizeTable, "html") %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
} else {
  cat("Sample size not selected.")
}
```


### **Normality Tests**


#### **Shapiro-Wilk Test**
```{r shapiroTable, echo = FALSE, results='asis'}
if (!is.null(params$shapiroData)) {
knitr::kable(params$shapiroData, format = "html") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
} else {
  cat("Shapiro-Wilk test not selected.")
}
```


#### **QQ-Plot**
```{r qqPlot, echo = FALSE, results='asis'}
if (!is.null(params$qqPlotGraph)) {
  print(params$qqPlotGraph)
} else {
  cat("QQ-Plot not selected.")
}
```


#### **Density Plot**
```{r densityPlot, echo = FALSE, results='asis'}
if (!is.null(params$densityPlot)) {
  print(params$densityPlot)
} else {
  cat("Density plot not selected.")
}
```


### **Homogeneity of Variance**

#### **Levene's Test**
```{r leveneTable, echo = FALSE, results='asis'}
if (!is.null(params$leveneData)) {
  knitr::kable(params$leveneData, format = "html") %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
} else {
  cat("Levene's test not selected.")
}
```


### **Log transformation?**

```{r log-transform-message, echo=FALSE, results='asis'}
if (!params$logTransformed) {
  cat("This data was ***not*** log transformed.")
} else {
  cat("This data was log transformed.")
}
```


### **Group Comparisons**
You selected a `r params$testName` test.


```{r comparison-results, echo=FALSE, results='asis'}
if (!is.null(params$testResultData)) {
  knitr::kable(params$testResultData, format = "html") %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
} else {
  cat("Group comparison test not selected.")
}
```


### **Post-Hoc Tests**
Reminder, post-hoc tests are only valid if the group comparison test has a p value < 0.05. `r params$postHocName`
```{r posthoc, echo=FALSE, results='asis'}
if (!is.null(params$posthocData)) {
  knitr::kable(params$posthocData, format = "html") %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
} else {
  cat("Post-hoc test not selected.")
}
```


#### **Compact Letter Notation**
Groups with the same letter are not significantly different from each other.
```{r cldTable, echo=FALSE, results='asis'}
if (!is.null(params$cldData)) {
  knitr::kable(params$cldData, format = "html") %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
} else {
  cat("Compact Letter Notation not selected.")
}
```

### **Contact**

If you have found any issues with this report, or want to suggest improvements, please contact the developer [Marnie](mailto:mlm715@uowmail.edu.au) or [email](mailto:mmaddock@uow.edu.au). Issues, or requests for features can also be added in the `Issues` tab on [GitHub](https://github.com/MarnieMaddock/FASTqPCR/issues). Note Colour Scheme suggestions for graphs can also be sent to [Marnie](mailto:mlm715@uowmail.edu.au?subject=FASTqPCR Colour Request&body=Hi, I have a colour scheme request. Here is a list of colours in order. Please use hex codes, e.g. #000000, #63b8ff:).

![](www/footer.svg)



